% resume template adapted from Aras Güngöre

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}

\usepackage{hyperref}
\hypersetup{
    colorlinks = true,
    allcolors = Brown,
}

\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\usepackage{ragged2e}
\usepackage[super]{nth}

\input{glyphtounicode}

\newcommand*{\doi}[1]{\href{http://dx.doi.org/#1}{doi:#1}}
\newcommand*{\arxiv}[1]{\href{http://arxiv.org/abs/#1}{arXiv:#1}}
\newcommand*{\biorxiv}[1]{\href{http://biorxiv.org/content/#1}{bioRxiv:#1}}
\newcommand*{\pubmed}[1]{\href{http://www.ncbi.nlm.nih.gov/pubmed/#1}{PMID:#1}}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage[T1]{fontenc}
\usepackage[bitstream-charter]{mathdesign}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubheading}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
        \ifx\relax#5\relax 
          \vspace{-7pt}
        \else
          \linebreak\textit{\small#5}
          \vspace{-3pt}
        \fi
}

\newcommand{\simpleHeading}[3]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} & \small#2 \\
    \end{tabular*}
    \ifx\relax#3\relax 
    \else
      \linebreak\textit{\small#3}
    \fi
    \vspace{-5pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.10in, rightmargin=0.10in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\justifying

\begin{center}
  \textbf{\Huge \scshape Jason Ken Adhinarta} \\ \vspace{3pt}
    \small
    \href{https://jasonkena.github.io}{jasonkena.github.io}
   \hspace{0.05cm}$\cdot$\hspace{0.05cm}
    \href{mailto:jason.adhinarta@bc.edu}{ jason.adhinarta@bc.edu }
   \hspace{0.05cm}$\cdot$\hspace{0.05cm}
    Chestnut Hill, MA
\end{center}

\section{Publications \textit{\small{(* indicates equal contribution)}}}
\vspace{3pt}
\resumeSubHeadingListStart
    \small{\item{
        
        \samepage{
          \hypertarget{hydra}{
            [A]
          }
          \textbf{Jason K. Adhinarta}*, Yutian Fan*, Michael Lin*, Richard Ren*, Micaela Roth*, Ayal Yakobe*, Shulin Zhang*, Rafael Yuste, Donglai Wei. \textbf{VesicleEM: A Comprehensive Vesicle Analysis Toolbox for Volumetric Electron Microscopy}. 
          \ifx\relaxManuscript in preparation\relax % Check if #5 is defined (empty)
          \else
            Manuscript in preparation.        
          \fi
           
         }
        
        \samepage{
          \hypertarget{hydra_bio}{
            [B]
          }
          Shulin Zhang, Netanel Ofer, Wataru Yamomoto, Richard Schalek, Yuelong Wu, Christoph Dupre, \textbf{Jason K. Adhinarta}, Yutian Fan, Michael Lin, Micaela Roth, Ben Cox, Celina Juliano, Donglai Wei, Jeff Lichtman, Rafael Yuste. \textbf{Connectomic analysis of the \textit{Hydra vulgaris} endoderm: cell types and vesicles}. 
          \ifx\relaxManuscript in preparation\relax % Check if #5 is defined (empty)
          \else
            Manuscript in preparation.        
          \fi
           
         }
        
        \samepage{
          \hypertarget{wormnd}{
            [C]
          }
          \textbf{Jason K. Adhinarta}*, Jizheng Dong*, Tianxiao He*, Junxiang Huang*, Daniel Sprague*, Jia Wan, Hyun Jee Lee, Zikai Yu, Hang Lu, Eviatar Yemini, Saul Kato, Erdem Varol, Donglai Wei. \textbf{WormND: A Benchmark for Extracting Whole-Brain Neural Dynamics of \textit{C. elegans} at the Neuron Resolution}. 
          \ifx\relaxManuscript under revision\relax % Check if #5 is defined (empty)
          \else
            Manuscript under revision.        
          \fi
           
         }
        
        \samepage{
          \hypertarget{freseg}{
            [D]
          }
          Shixuan Gu, \textbf{Jason K. Adhinarta}, Mikhail Bessmeltsev, Jiancheng Yang, Jessica Zhang, Wenjie Yin, Daniel Berger, Jeff W. Lichtman, Hanspeter Pfister, Donglai Wei. \textbf{Frenet-Serret Frame-based Decomposition for Part Segmentation of 3D Curvilinear Structures}. 
          \ifx\relaxUnder review at IEEE Transactions on Medical Imaging\relax % Check if #5 is defined (empty)
          \else
            Under review at IEEE Transactions on Medical Imaging.        
          \fi
           \arxiv{2404.14435}
         }
        
        \samepage{
          \hypertarget{trisam}{
            [E]
          }
          Jia Wan, Wanhua Li, \textbf{Jason K. Adhinarta}, Atmadeep Banerjee, Evelina Sjostedt, Jingpeng Wu, Jeff Lichtman, Hanspeter Pfister, Donglai Wei. \textbf{TriSAM: Tri-Plane SAM for zero-shot cortical blood vessel segmentation in VEM images}. 
          \ifx\relaxUnder review at IEEE Journal of Biomedical and Health Informatics\relax % Check if #5 is defined (empty)
          \else
            Under review at IEEE Journal of Biomedical and Health Informatics.        
          \fi
           \arxiv{2401.13961v4}
         }
        
        \samepage{
          \hypertarget{xiaomeng}{
            [F]
          }
          Xiaomeng Han, Xiaotang Lu, Peter H. Li, Shuohong Wang, Richard Schalek, Yaron Meirovitch, Zudi Lin, \textbf{Jason K. Adhinarta}, Daniel Berger, Yuelong Wu, Tao Fang, Elif S. Meral, Shadnan Asraf, Hidde Ploegh, Hanspeter Pfister, Donglai Wei, Viren Jain, James S. Trimmer, Jeff W. Lichtman. \textbf{Multiplexed Volumetric CLEM enabled by antibody derivatives provides new insights into the cytology of the mouse cerebellar cortex}. 
          \ifx\relaxNature Communications 2024\relax % Check if #5 is defined (empty)
          \else
            Nature Communications 2024.        
          \fi
           \doi{10.1038/s41467-024-50411-z} \pubmed{39103318}
         }
        
        \samepage{
          \hypertarget{imheart}{
            [G]
          }
          Jiancheng Yang, Ekaterina Sedykh, \textbf{Jason K. Adhinarta}, Hieu Le, Pascal Fua. \textbf{Generating Anatomically Accurate Heart Structures via Neural Implicit Fields}. 
          \ifx\relaxMedical Image Computing and Computer-Assisted Intervention 2024\relax % Check if #5 is defined (empty)
          \else
            Medical Image Computing and Computer-Assisted Intervention 2024.        
          \fi
           \doi{10.1007/978-3-031-72378-0\_25}
         }
        
        \samepage{
          \hypertarget{ribseg}{
            [H]
          }
          Liang Jin, Shixuan Gu, Donglai Wei, \textbf{Jason K. Adhinarta}, Kaiming Kuang, Yongjie J. Zhang, Hanspeter Pfister, Bingbing Ni, Jiancheng Yang, Ming Li. \textbf{RibSeg v2: A Large-scale Benchmark for Rib Labeling and Anatomical Centerline Extraction}. 
          \ifx\relaxIEEE Transactions on Medical Imaging 2023\relax % Check if #5 is defined (empty)
          \else
            IEEE Transactions on Medical Imaging 2023.        
          \fi
           \doi{10.1109/TMI.2023.3313627} \pubmed{37695967}
         }
        
        \samepage{
          \hypertarget{phosphor}{
            [I]
          }
          \textbf{Jason K. Adhinarta}, Eric Jobiliong, Muhandis Shiddiq, Henri P. Uranus and Eden Steven. \textbf{Light storage and thermal-assisted switching of SrAl\textsubscript{2}O\textsubscript{4}:Eu\textsuperscript{2+}, Dy\textsuperscript{3+}}. 
          \ifx\relaxJournal of Nonlinear Optical Physics \& Materials 2019\relax % Check if #5 is defined (empty)
          \else
            Journal of Nonlinear Optical Physics \& Materials 2019.        
          \fi
           \doi{10.1142/S0218863519500425}
         }
        
    }}
\resumeSubHeadingListEnd



\section{Patents}
\vspace{3pt}
\resumeSubHeadingListStart
    \small{\item{
        
        \samepage{
          \hypertarget{mycelium}{
            [J]
          }
          Eden Steven, Ray A. O. Sinurat, Alvius Tinambunan, Edmund F. Anderson, Calvin, Andrew D. Widjaja, Josavan Ezekhiel, \textbf{Jason K. Adhinarta}. \textbf{A Robotic Method of Monitoring, Hydrating, Training, and Treating Bacterial or Fungal Infections of New-growth Fungal Cultures to Produce Densified Sheet-like Lateral Networks of Fungal Materials}. \href{https://jasonkena.github.io/static/patent.pdf}{PDKI:P00202009416}. Patent pending, submitted to Indonesian patent registry in 2020
        }
        
    }}
\resumeSubHeadingListEnd


\end{document}
