% resume template adapted from Aras Güngöre

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}

\usepackage{hyperref}
\hypersetup{
    colorlinks = true,
    allcolors = Brown,
}

\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\usepackage{ragged2e}
\usepackage[super]{nth}
\usepackage{expl3}



\ExplSyntaxOn
% Define the custom command
\NewDocumentCommand{\customcommand}{mm}{
    \int_zero:N \l_tmpa_int % Reset the counter
    % Parse the input lists
    \seq_set_split:Nnn \l_tmpa_seq { , } { #1 } % First list
    \seq_set_split:Nnn \l_tmpb_seq { , } { #2 } % Second list

    % Ensure both lists have the same length
    \int_compare:nNnTF {\seq_count:N \l_tmpa_seq} = {\seq_count:N \l_tmpb_seq}
        {
            % If lengths match, generate hyperlinks
          [\seq_mapthread_function:NNN \l_tmpa_seq \l_tmpb_seq \__customcommand_generate_hyperlink:nn]
        }
        {
            % If lengths don't match, throw an error
            \textbf{Error: Lists must have the same length!}
        }
}

\cs_new_protected:Nn \__customcommand_generate_hyperlink:nn {
    \int_incr:N \l_tmpa_int % Increment the counter
    \hyperlink{#1}{#2}%
    % Add a comma and space unless this is the last item
    \int_compare:nNnT {\l_tmpa_int} < {\seq_count:N \l_tmpa_seq}
        {,~}
}

\ExplSyntaxOff


\input{glyphtounicode}

\newcommand*{\doi}[1]{\href{http://dx.doi.org/#1}{doi:#1}}
\newcommand*{\arxiv}[1]{\href{http://arxiv.org/abs/#1}{arXiv:#1}}
\newcommand*{\biorxiv}[1]{\href{http://biorxiv.org/content/#1}{bioRxiv:#1}}
\newcommand*{\pubmed}[1]{\href{http://www.ncbi.nlm.nih.gov/pubmed/#1}{PMID:#1}}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage[T1]{fontenc}
\usepackage[bitstream-charter]{mathdesign}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
% \addtolength{\oddsidemargin}{-0.5in}
% \addtolength{\evensidemargin}{-0.5in}
% \addtolength{\textwidth}{1in}
% \addtolength{\topmargin}{-.5in}
% \addtolength{\textheight}{1.0in}
\addtolength{\oddsidemargin}{-0.25in}
\addtolength{\evensidemargin}{-0.25in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


\newcommand{\dualsectionold}[2]{%
  \noindent
    \parbox[b]{0.5\textwidth}{\raggedright\scshape\large #1}%
    \hfill
    \parbox[b]{0.5\textwidth}{\raggedleft\scshape\large #2}%
}
\newcommand{\dualsectionhline}{%
  \vspace{2pt}\color{black}\titlerule\vspace{-5pt}
}
  
\newcommand{\dualsection}[2]{%
  \dualsectionold{#1}{#2}%
  \vspace{-5pt}\dualsectionhline
}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubheading}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
        \ifx\relax#5\relax 
          \vspace{-7pt}
        \else
          \linebreak\textit{\small#5}
          \vspace{-3pt}
        \fi
}

\newcommand{\simpleHeading}[3]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} & \small#2 \\
    \end{tabular*}
    \ifx\relax#3\relax 
    \else
      \linebreak\textit{\small#3}
    \fi
    \vspace{-5pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.10in, rightmargin=0.10in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\justifying

\begin{center}
  \textbf{\Huge \scshape Personal Experience} \\ \vspace{3pt}
    \small
    \href{https://jasonkena.github.io}{jasonkena.github.io}
   \hspace{0.05cm}$\cdot$\hspace{0.05cm}
    \href{mailto:jason.adhinarta@bc.edu}{ jason.adhinarta@bc.edu }
   \hspace{0.05cm}$\cdot$\hspace{0.05cm}
    Chestnut Hill, MA
\end{center}


\dualsection{Jason Ken Adhinarta}{University of Maryland}
\vspace{2pt}\color{black}\titlerule%\vspace{-5pt}


Since Fall 2023, I have been \textbf{remotely advising highschool students} at Sekolah Pelita Harapan in Tangerang, Indonesia through the Applied Science Academy. This year, I am supporting a sophomore passionate about autonomous vehicles. It was through the same program that I found my passion for computer vision, and I am humbled to now support his growth in robotics. Months ago, we brainstormed building a remote-controlled car with a mounted camera for spatial navigation using neural radiance fields. Recently, he set up the controls and began feeding footage into Nerfstudio.

Engaging with these students has reinforced my dedication to making education accessible---a commitment shaped by my own experiences as a \textbf{first-generation American}. I am grateful for the full-tuition scholarship and need-based aid that made my undergraduate studies possible, and I have taken on research or teaching roles every semester at Boston College to cover the remaining costs. \textbf{I aspire to become a professor}, melding research and teaching to support others facing similar barriers.

A PhD in Computer Science at UMD is a step toward this goal. Complementing my research, I look forward to contributing through teaching, whether by inspiring highschool students through the \textbf{TRAILS AI Summer Academy} or by serving as a TA for \textbf{CMSC 426: Computer Vision.}

\end{document}
